Thermodynamic fragments in magic state theories

### 2021-01-20 magic_paper.tex
added first elbow coordinates for n-copy. Will add more details tomorrow. Need to teak first elbow condition

Consider the simple energy spectrum 
\begin{equation}
	(E_0, E_1, E_2) = (1,0,0).
\end{equation}
Then, $Z = 2 + e^{-\beta}$.
Furthermore, for clarity, let $\chi \coloneqq \frac{1}{6}-\frac{1}{18}\epsilon$ be the positive and $-\nu \coloneqq -\frac{1}{3} + \frac{4}{9}\epsilon$ the negative Wigner components of $\noisys(\epsilon)$.
The 1-copy Wigner distributions in this scenario are depicted in~\cref{tab:thermal_w}.
\begin{table}[h]
  \def\arraystretch{2}
  \centering
  \begin{tabular}{c|c|c|c}
    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma}(\bmx)$ & $\tilde{\bmw}$ \\
    \hline
    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta}}{3Z}$ & $\displaystyle 3Z \chi e^{\beta}$ \\
    \hline
    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \chi$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z \chi$ \\
    \hline
    $(2,2)$ & $\displaystyle -\nu$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z (-\nu)$ \\
    \hline
  \end{tabular}
  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\tilde{\bmw}$ listed in order of decreasing slope (holds for all temperatures $\beta^{-1}$).}
  \label{tab:thermal_w}
\end{table}

To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply add up the Wigner components in order of decreasing slope $\tilde{\bmw} \coloneqq W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
The first elbow of the 1-copy Lorenz curve is
\begin{equation}
	(x_0, L_0) = \left( \frac{e^{-\beta}}{Z}, 3\chi \right).
\end{equation}

Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
\begin{equation}
	\widetilde{\bmw\too{n}} = \frac{W_{\noisys\too{n}}(\bmx)}{W_{\gamma\too{n}}(\bmx)} = \left( \frac{W_{\noisys}(\bmx)}{W_{\gamma}(\bmx)} \right)\too{n} = \widetilde{\bmw}\too{n}.
\end{equation}

According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to sort $\widetilde{\bmw\too{n}}$ in decreasing order and take the cumulative sum of the corresponding components $W_{\noisys\too{n}}(\bmx)$ and $W_{\gamma\too{n}}(\bmx)$.

We can therefore construst a trinomial generating function that returns the values and the multiplicities of the distinct Wigner components for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment.
\begin{equation}
	\tilde{w}(X,Y) \coloneqq (3Z)^n (-\nu + 5\chi X + 3\chi e^\beta Y)^n
\end{equation}
There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms ($i,j = 0,\dots,n$ with $i+j \leq n$) with the coefficients of these terms representing the multiplicities and values of the different ratios.

We can inductively show that the ``start of the Lorenz curve'' corresponds to $\nu^n$ for even $n$ and $\nu^(n-1) \chi e^\beta$ for 
\begin{equation}
	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}
\end{equation}
\nick{Not good enough to restrict to the start of the curve (show why)}

\nick{coordinate generating functions}

In order to construct the 2-copy Lorenz curve, we first obtain the 2-copy Wigner distribution as a convolution of the 1-copy Wigner distribution (between two identical systems A and B) and then take again the cumulative sum of the Wigner components in order of decreasing slope $W_{\noisys\too{2}}(\bmx_A \oplus \bmx_B)/W_{\gamma_\beta\too{2}}(\bmx_A \oplus \bmx_B)$.
This order, hence the first elbow depends on the temperature,
\begin{equation}
	(x_0, L_0) = 
	\begin{cases}
		\left( \frac{1}{9(2+e^{-\beta})^2}, \left(\frac{1}{3} - \frac{4}{9}\epsilon \right)^2 \right),\ &\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}, \\
		\left( \frac{1}{(1+2e^\beta)^2}, \left(\frac{1}{2} - \frac{1}{6}\epsilon \right)^2 \right),\ &\beta \geq \ln{\left(8-\frac{18}{3-\epsilon}\right)}.
	\end{cases}
\end{equation}

\nick{Unfortunately, performing the same calculation as in~\cref{eq:constraint_deriv} for $\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}$, yields a very loose bound.
The first elbow is not a good indicator in this case, points closer to the peak intersect first.}

For a qutrit, let the energy spectrum be $E_0 \geq E_1 \geq E_2$. 
Then, we can explicitly write the thermal Wigner distribution as
\begin{equation}
	\W{\gamma_\beta} = \frac{1}{3E_\beta} \big( \overbrace{e^{-\beta E_0}}^3, \overbrace{e^{-\beta E_1}}^3, \overbrace{e^{-\beta E_2}}^3 \big),
\end{equation}
which is sorted in decreasing order.
We choose the Strange state where the negativity is in the first component of its Wigner distribution
\begin{equation}\label{eq:wsu}
	\W{\noisys(\epsilon)} = \Bigg( \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1, \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon}^8\Bigg),
\end{equation}

However, higher copies are not sorted, for example
\begin{equation}
	\begin{split}
	\W{\gamma_\beta\too{2}} = \frac{1}{9E_\beta^2} \Bigg( &\overbrace{\overbrace{e^{-\beta 2E_0}}^3, \overbrace{e^{-\beta (E_0 + E_1)}}^3, \overbrace{e^{-\beta (E_0 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_1 + E_0)}}^3, \overbrace{e^{-\beta 2E_1}}^3, \overbrace{e^{-\beta (E_1 + E_2)}}^3}^3, \\
	 &\overbrace{\overbrace{e^{-\beta (E_2 + E_0)}}^3, \overbrace{e^{-\beta (E_2 + E_1)}}^3, \overbrace{e^{-\beta 2E_2}}^3}^3 \Bigg).
	\end{split}
\end{equation}
\ddd{[Definitely impressed by this Latexing...but perhaps just give the multiplicities and spectrum values. I.e. ``(blah) with multiplicity (blah) and ...'']} \nick{So the problem is that the exact position of each component matters, e.g. thermal state component $e^{-\beta 2E_0}$ corresponds to a positive Strange state component in one position and a negative Strange state component in another.} 
For the Strange state we have
\begin{equation}
	\begin{split}
	\W{\noisys(\epsilon)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^2}^1, \overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^{8}, \\
	&\overbrace{\overbrace{ \left( -\frac{1}{3} + \frac{4}{9}\epsilon \right) \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)}^1, \overbrace{\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^2}^8}^8,  \Bigg).
	\end{split}
\end{equation}
\nick{We need to sort the distributions $\W{\gamma_\beta\too{2}}, \W{\noisys(\epsilon)\too{2}}$, so that the vector
\begin{equation}
	\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\noisys(\epsilon)\too{2}})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{81}}{(\W{\sigma})_{81}} \right)^T,
\end{equation}
is in decreasing order, i.e. $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
Then, we need to generalise for any number of copies $n$}

>>>>

Consider the simple energy spectrum 
\begin{equation}
	(E_0, E_1, E_2) = (1,0,0).
\end{equation}
Then, $Z = 2 + e^{-\beta}$.
Furthermore, for clarity, let $\chi \coloneqq \frac{1}{6}-\frac{1}{18}\epsilon$ be the positive and $-\nu \coloneqq -\frac{1}{3} + \frac{4}{9}\epsilon$ the negative Wigner components of $\noisys(\epsilon)$.
The 1-copy Wigner distributions in this scenario are depicted in~\cref{tab:thermal_w}.
\begin{table}[h]
  \def\arraystretch{2}
  \centering
  \begin{tabular}{c|c|c|c}
    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma}(\bmx)$ & $\tilde{\bmw}$ \\
    \hline
    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \chi$ & $\displaystyle \frac{e^{-\beta}}{3Z}$ & $\displaystyle 3Z \chi e^{\beta}$ \\
    \hline
    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \chi$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z \chi$ \\
    \hline
    $(2,2)$ & $\displaystyle -\nu$ & $\displaystyle \frac{1}{3Z}$ & $\displaystyle 3Z (-\nu)$ \\
    \hline
  \end{tabular}
  \caption{Wigner components $W_{\gamma}(\bmx)$, $W_{\noisys}(\bmx)$ and the associated slope $\widetilde{\bmw}$ listed in order of decreasing slope (holds for all temperatures $\beta^{-1}$).}
  \label{tab:thermal_w}
\end{table}

To construct the 1-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$, we simply add up the Wigner components in order of decreasing slope $\widetilde{\bmw} \coloneqq W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
The first elbow of the 1-copy Lorenz curve is
\begin{equation}
	(x_0, L_0) = \left( \frac{e^{-\beta}}{Z}, 3\chi \right).
\end{equation}

As illustrated in~\cref{tab:thermal_w}, the phase space can be split into three regions, based on the different values of the slope $\widetilde{\bmw}$.
As more copies ($n>1$) are considered, the system is described by higher dimensional phase spaces which contains more regions of different slope.
Notice that the slope of the $n$-copy Lorenz curve can be expressed as a self-convolution of the 1-copy Lorenz curve slope $n$ times,
\begin{equation}
	\widetilde{\bmw\too{n}} = \frac{\W{\noisys\too{n}}[\bmx]}{\W{\gamma\too{n}}[\bmx]} = \left( \frac{\W{\noisys}[\bmx]}{\W{\gamma}[\bmx]} \right)\too{n} = \widetilde{\bmw}\too{n}.
\end{equation}
Therefore, the regions of different slope in an $n$-copy phase space are generated by the 1-copy phase space regions.
The process is outlined below.

According to~\cref{def:lc}, to construct the $n$-copy Lorenz curve, we need to evaluate the components of $\widetilde{\bmw\too{n}}$, sort them in decreasing order and take the cumulative sum of the corresponding components $\W{\noisys\too{n}}[\bmx]$ and $\W{\gamma\too{n}}[\bmx]$.

To evaluate the distinct components and multiplicities of $\widetilde{\bmw\too{n}}, \W{\noisys\too{n}}[\bmx], \W{\gamma\too{n}}[\bmx]$, we can construct trinomial generating functions.
In particular, for a general $n$-copy $\epsilon$-noisy Strange state in a $\gamma_\beta$-fragment, we can use~\cref{tab:thermal_w} to construct the following generating functions,
\begin{align}
	&G(X,Y; \noisys) \coloneqq (-\nu + 5\chi X + 3\chi Y)^n \nonumber\\
	&= \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} \big] X^i Y^j, \\
	&G(X,Y; \gamma) \coloneqq \left( \frac{1}{3Z} + 5\frac{1}{3Z} X + 3 \frac{e^{-\beta}}{3Z} Y \right)^n \nonumber\\
	&= (3Z)^{-n} \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} e^{-j\beta} X^i Y^j, \\
	&G(X,Y; \widetilde{\bmw}) \coloneqq \Big( 3Z(-\nu) + 5(3Z\chi) X + 3(3Z\chi) e^\beta Y \Big)^n \nonumber\\
	&= (3Z)^n \sum\limits_{\substack{i,j = 0,\dots,n \\ i+j \leq n}} m_{ij} \big[(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \big] X^i Y^j,
\end{align}
where the $(i,j)$-th term multiplicity $m_{ij}$ is given by
\begin{equation}
	m_{ij} \coloneqq \frac{n!}{i!j!(n-i-j)!} 5^i 3^j.
\end{equation}
There are $\frac{(n+1)(n+2)}{2}$ distinct $X^i Y^j$ terms. 
Each term $X^i Y^j$ represents a phase space region with different slope. 
Consider the generating function $G(X,Y;\widetilde{\bmw})$ for the slope. 
The coefficient in front of the term is a product of the multiplicity $m_{ij}$ and the value of the slope in the region, $(-\nu)^{n-i-j} \chi^{i+j} e^{j\beta}$.
To find the value of the Wigner components $\W{\noisys\too{n}}(\bmx), \W{\gamma\too{n}}(\bmx)$ in this phase space region, we simply read the coefficients of the term $X^i Y^j$ in functions $G(X,Y; \noisys), G(X,Y; \gamma)$ respectively.

For example, the 2-copy case gives
\begin{equation}
	\begin{split}
	&G(\widetilde{\bmw\too{2}}; X,Y) = 9Z^2 \Big( 1(\nu^2) + 10(-\nu \chi)X + 6(-\nu \chi e^\beta) Y + \\
	&30 (\chi^2 e^\beta) XY + 25(\chi^2)X^2 + 9(\chi^2 e^{2\beta})Y^2 \Big).
	\end{split}
\end{equation}
The expression contains six different terms corresponding to the different phase space regions.
Each term (e.g. $X$) has a coefficient that consists of the multiplicity, i.e. the number of phase space points contained in the corresponding region, (e.g. $10$) and the value of the slope at the points of the region (e.g. $9Z^2(-\nu \chi)$).

We want to calculate the coordinates of the first elbow of the $n$-copy Lorenz curve $\lc{\noisys(\epsilon)}{\gamma_\beta}$.
To do this, we first need to find the highest slope value, i.e. find
\begin{equation}
	\widetilde{\bmw}_{\rm{max}} = \max{\{ (-\nu)^{n-i-j} \chi^{i+j} e^{j\beta} \}_{i,j}}.
\end{equation}
For even $n$,
\begin{equation}
	\widetilde{\bmw}_{\rm{max}} = \max{\{ \nu^n, \chi^n e^{n\beta} \}}.
\end{equation}
The final optimisation depends on the temperature regime, we work in.
Specifically, $\widetilde{\bmw}_{\rm{max}} =  \nu^n$ for
\begin{equation}\label{eq:temp_regime}
	\beta \leq \ln{\left(8-\frac{18}{3-\epsilon}\right)}
\end{equation}
This value of slope corresponds to term $X^0Y^0 = 1$, so the Lorenz curve coordinates are
\begin{equation}
	(x_0, L_0) = \Big( (3Z)^{-n}, \nu^n \Big).
\end{equation}

\nick{Not good enough. For curves to intersect must have such high noise that condition~\cref{eq:temp_regime} does not hold anymore. Need to tweak.}
